resistanceModelNotesAndy

### 2015-03-23 resistanceModelNotesAndy.Rmd
progress notes
noting progress

**19/3/15** sat 10.15-2.15 4hrs

@@

@@

>>>>

**20/3/15** sat 10.15-2.15 4hrs

@@

**22/3/15** mon 9.45

@@

sort this
To git@github.com:AndySouth/resistance.git
 ! [rejected]        master -> master (non-fast-forward)
error: failed to push some refs to 'git@github.com:AndySouth/resistance.git'
hint: Updates were rejected because the tip of your current branch is behind
hint: its remote counterpart. Integrate the remote changes (e.g.
hint: 'git pull ...') before pushing again.
hint: See the 'Note about fast-forwards' in 'git push --help' for details.
